Concurrent Programming with CXL

### 2020-05-21 book/paper.tex
Latest

While correct, it is not considered a good solution.
The solution is an example of what is called \emph{busy waiting}:
processes spin in a loop until some desirable condition is met.
The astute reader might wonder if obtaining an ordinary lock itself is an
example of busy waiting.  After all, the CXL \texttt{synch} implementation
of \texttt{lock()} spins in a loop until the lock is available
(see Figure~\ref{fig:locks}).

@@

So it is considered ok to have processes busy wait for a lock to become
available, but not to busy wait for application-specific conditions.

>>>>

While correct, it is not considered a good solution.
The solution is an example of what is called \emph{busy-waiting}:
processes spin in a loop until some desirable condition is met.
The astute reader might wonder if obtaining an ordinary lock itself is an
example of busy-waiting.  After all, the CXL \texttt{synch} implementation
of \texttt{lock()} spins in a loop until the lock is available
(see Figure~\ref{fig:locks}).

@@

\begin{figure}
\begin{code}
\verbatiminput{../RWlock.cxl}
\end{code}
\caption{Reader/Writer with Two Locks.}
\label{fig:rw2lock}
\end{figure}

So it is considered ok to have processes using spinlock a implement a
lock, but not to busy-wait for application-specific conditions.

Figure~\ref{fig:rw2lock} presents a reader/writer lock implementation
that does not busy-wait.
It uses two locks: \texttt{rwlock} is used by both readers and writers,
while \texttt{rlock} is only used by readers.
